SRG operator evolution

### 2019-05-31 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updates to SRG operator evolution notes.
Further updates to the outline. Splitting results sections by non-local, semi-local, and local potentials. Also, adding a section for details of calculations where momentum and weights can be confusing.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Building SRG unitary transformations}
\label{sec:srg_unitary_transformations}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Operator evolution}
\label{sec:operator_evolution}

Organize this according to the figures: what story do the figures tell? Format should be description of the calculation, followed by the figure, followed by takeaways.
\\

Add the following figures: momentum projection operator figures with accompanying momentum distributions for SRG transformations from N$^3$LO non-local potential \cite{Entem:2003ft}, N$^3$LO or N$^4$LO semi-local potentials \cite{Reinert:2017usi}, and N$^2$LO local potentials \cite{Gezerlis:2014zia}.
\\

% Entem-Machleidt N3LO results

@@

@@

% Gez. et al. N2LO results

>>>>

\tableofcontents

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mathematical/computational details}
\label{sec:math_comp_details}

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Building SRG unitary transformations}
\label{sec:srg_unitary_transformations}

@@

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Momentum projection operator: $a^{\dagger}_q a_q$}
\label{sec:momentum_proj_operator}

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Momentum distribution function: $\phi^2$}
\label{sec:momentum_dist_funcs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

Organize this according to the figures: what story do the figures tell? Format should be description of the calculation, followed by the figure, followed by takeaways.

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Entem-Machleidt N$^3$LO non-local potential}
\label{sec:nonlocal_results}

@@

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{RKE N$^3$LO and N$^4$LO semi-local potentials}
\label{sec:semilocal_results}

@@

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Gezerlis N$^2$LO local potentials}
\label{sec:local_results}
